---
pagetitle: "Campsis NCA"
date: ""
author: ""
output: github_document
always_allow_html: true
---

# campsisnca
Analyse your simulation output using non-compartmental analysis.

## Installation
Install the latest stable release as follows:
  
```{r, eval=FALSE}
devtools::install_github("Calvagone/campsisnca")
```

## Basic use

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
rich_sampling <- c(0,1,2,4,6,8,12,16,24)
day1 <- rich_sampling
day2day6 <- c(2,3,4,5,6)*24
day7 <- rich_sampling + 6*24
day8day10 <- c(8,9,10)*24

ds <- Dataset(200) %>%
  add(Bolus(time=(0:6)*24, amount=1000)) %>%
  add(Observations(times=c(day1, day2day6, day7, day8day10))) %>%
  add(Covariate("BW", UniformDistribution(50,100)))

model <- model_suite$testing$nonmem$advan4_trans4
cl <- model %>% find(Equation("CL"))
model <- model %>% replace(Equation("CL", paste0(cl@rhs, "*pow(BW/70, 0.75)")))

campsis <- model %>% simulate(dataset=ds, dest="rxode2", seed=1, outvars="BW")
```

First import the `campsisnca` and `gtsummary` packages as follows:

```{r, message=FALSE}
library(campsisnca)
library(gtsummary)
```

### Example 1: PK metrics at Day 1 and Day 7

Assume some results were simulated with Campsis (see `campsis` dataframe) :

```{r, message=FALSE}
campsis
```

Let's calculate PK metrics at Day 1 and Day 7 as follows:

```{r, message=FALSE}
# Day 1
ncaD1 <- NCAMetrics(x=campsis %>% timerange(0, 24), variable="Y", scenario=c(day="Day 1")) %>%
  add(c(Auc(unit="ng/mL*h"), Cmax(unit="ng/mL"), Tmax(unit="h"), Ctrough(unit="ng/mL"))) %>%
  calculate()

# Day 7 
ncaD7 <- NCAMetrics(x=campsis %>% timerange(144, 168, rebase=TRUE), variable="Y", scenario=c(day="Day 7")) %>%
  add(c(Auc(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()
```

These 2 metrics may be imported into a metrics table object, as follows:

```{r, message=FALSE}
table <- NCAMetricsTable(unitLineBreak=TRUE)  
table <- table %>%
  add(c(ncaD1, ncaD7))
```

This table can be exported:

1. To a dataframe using the `export` function:

```{r, message=FALSE}
table %>% export(dest="dataframe")
```

2. To a HTML table using `gt`:

```{r, message=FALSE}
table %>% export(dest="gt", subscripts=TRUE)
```

Please note the individual metrics can also be exported to  a dataframe using the `export` function as follows:

```{r, message=FALSE}
table %>% export(dest="dataframe", type="individual")
```

### Example 2: PK metrics at Day 1 and Day 7 for different body weight ranges

```{r, message=FALSE}
library(dplyr)
campsis_bw_50_75 <- campsis %>% filter(BW > 50 & BW < 75)
campsis_bw_75_100 <- campsis %>% filter(BW >= 75 & BW < 100)

scenarioD1_a <- c(day="Day 1", bw_range="BW range: 50-75")
ncaD1_a <- NCAMetrics(x=campsis_bw_50_75 %>% timerange(0, 24), variable="Y", scenario=scenarioD1_a) %>% 
  add(c(Auc(unit="ng/mL*h"), Cmax(unit="ng/mL"), Tmax(unit="h"), Ctrough(unit="ng/mL"))) %>%
  calculate()

scenarioD7_a <- c(day="Day 7", bw_range="BW range: 50-75")
ncaD7_a <- NCAMetrics(x=campsis_bw_50_75 %>% timerange(144, 168, rebase=T), variable="Y", scenario=scenarioD7_a) %>%
  add(c(Auc(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()

scenarioD1_b <- c(day="Day 1", bw_range="BW range: 75-100")
ncaD1_b <- NCAMetrics(x=campsis_bw_75_100 %>% timerange(0, 24), variable="Y", scenario=scenarioD1_b) %>%
  add(c(Auc(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()

scenarioD7_b <- c(day="Day 7", bw_range="BW range: 75-100")
ncaD7_b <- NCAMetrics(x=campsis_bw_75_100 %>% timerange(144, 168, rebase=T), variable="Y", scenario=scenarioD7_b) %>%
  add(c(Auc(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()

table <- NCAMetricsTable(unitLineBreak=TRUE) %>%
  add(c(ncaD1_a, ncaD7_a, ncaD1_b, ncaD7_b))
table %>% export(dest="gt", subscripts=TRUE)
```

### Example 3: Calculate 2-compartment half-life metrics

```{r, message=FALSE}
nca <- NCAMetrics(x=campsis %>% mutate(DOSE=1000, TAU=24), variable="Y") %>%
  add(c(Thalf.2cpt.dist(), Thalf.2cpt.eff(), Thalf.2cpt.z())) %>%
  calculate()

table <- NCAMetricsTable() %>%
  add(nca)
table %>% export(dest="gt", subscripts=TRUE)
```

### Example 4: Compute terminal half-live based on data

```{r, message=FALSE}
nca <- NCAMetrics(x=campsis, variable="Y") %>%
  add(c(Thalf(x=campsis %>% timerange(7*24, 10*24)))) %>%
  calculate()

table <- NCAMetricsTable() %>%
  add(nca)
table %>% export(dest="gt", subscripts=TRUE)
```
