---
pagetitle: "Campsis NCA"
date: ""
author: ""
output: github_document
always_allow_html: true
---

# campsisnca
Analyse your simulation output using non-compartmental analysis.

## Installation
Install the latest stable release as follows:
  
```{r, eval=FALSE}
devtools::install_github("Calvagone/campsisnca")
```

## Basic use

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
rich_sampling <- c(0,1,2,4,6,8,12,16,24)
day1 <- rich_sampling
day2day6 <- c(2,3,4,5,6)*24
day7 <- rich_sampling + 6*24
day8day10 <- c(8,9,10)*24

ds <- Dataset(200) %>%
  add(Bolus(time=(0:6)*24, amount=1000)) %>%
  add(Observations(times=c(day1, day2day6, day7, day8day10))) %>%
  add(Covariate("BW", UniformDistribution(50,100)))

model <- model_suite$testing$nonmem$advan4_trans4
cl <- model %>% find(Equation("CL"))
model <- model %>% replace(Equation("CL", paste0(cl@rhs, "*pow(BW/70, 0.75)")))

campsis <- model %>% simulate(dataset=ds, dest="rxode2", seed=1, outvars="BW")
```

First import the `campsisnca` and `gtsummary` packages as follows:

```{r, message=FALSE}
library(campsisnca)
library(gtsummary)
library(gt)
```

### Example 1: PK metrics at Day 1 and Day 7

Assume some results were simulated with Campsis (see `campsis` dataframe) :

```{r, message=FALSE}
campsis
```

Let's calculate PK metrics at Day 1 and Day 7 as follows:

```{r, message=FALSE}
# Day 1
ncaD1 <- NCAMetrics(x=campsis %>% timerange(0, 24), variable="Y", scenario=c(day="Day 1")) %>%
  add(c(AUC(unit="ng/mL*h"), Cmax(unit="ng/mL"), Tmax(unit="h"), Ctrough(unit="ng/mL"))) %>%
  calculate()

# Day 7 
ncaD7 <- NCAMetrics(x=campsis %>% timerange(144, 168, rebase=TRUE), variable="Y", scenario=c(day="Day 7")) %>%
  add(c(AUC(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()
```

These 2 metrics may be imported into a metrics table object, as follows:

```{r, message=FALSE}
table <- NCAMetricsTable() %>%
  add(c(ncaD1, ncaD7))
```

This table can be exported:

1. To a dataframe using the `export` function:

```{r, message=FALSE}
table %>% export(dest="dataframe")
```

When `type` is not specified, default value is `summary`. Argument `type` can also be `summary_wide` or `summary_pretty`. In the latter case, summary statistics are exported according to the arguments `stat_display` and `digits` provided for each metric.

2. To an HTML table using `gt`:

```{r, message=FALSE}
table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()
```

Please note the individual metrics can also be exported to  a dataframe using the `export` function as follows:

```{r, message=FALSE}
table %>% export(dest="dataframe", type="individual_wide")
```

### Example 2: PK metrics at Day 1 and Day 7 for different body weight ranges

```{r, message=FALSE}
library(dplyr)
campsis_bw_50_75 <- campsis %>% filter(BW > 50 & BW < 75)
campsis_bw_75_100 <- campsis %>% filter(BW >= 75 & BW < 100)

scenarioD1_a <- c(day="Day 1", bw_range="BW range: 50-75")
ncaD1_a <- NCAMetrics(x=campsis_bw_50_75 %>% timerange(0, 24), variable="Y", scenario=scenarioD1_a) %>% 
  add(c(AUC(unit="ng/mL*h"), Cmax(unit="ng/mL"), Tmax(unit="h"), Ctrough(unit="ng/mL"))) %>%
  calculate()

scenarioD7_a <- c(day="Day 7", bw_range="BW range: 50-75")
ncaD7_a <- NCAMetrics(x=campsis_bw_50_75 %>% timerange(144, 168, rebase=T), variable="Y", scenario=scenarioD7_a) %>%
  add(c(AUC(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()

scenarioD1_b <- c(day="Day 1", bw_range="BW range: 75-100")
ncaD1_b <- NCAMetrics(x=campsis_bw_75_100 %>% timerange(0, 24), variable="Y", scenario=scenarioD1_b) %>%
  add(c(AUC(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()

scenarioD7_b <- c(day="Day 7", bw_range="BW range: 75-100")
ncaD7_b <- NCAMetrics(x=campsis_bw_75_100 %>% timerange(144, 168, rebase=T), variable="Y", scenario=scenarioD7_b) %>%
  add(c(AUC(), Cmax(), Tmax(), Ctrough())) %>%
  calculate()

table <- NCAMetricsTable() %>%
  add(c(ncaD1_a, ncaD7_a, ncaD1_b, ncaD7_b))
table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()
```

```{r, message=FALSE}
# Alternatively, first stratification variable can be seen in columns (use of 'tbl_merge' within gtsummary)
table %>% export(dest="gt", subscripts=TRUE, combine_with="tbl_merge") %>% as_raw_html()
```

### Example 3: Calculate 2-compartment half-life metrics

```{r, message=FALSE}
nca <- NCAMetrics(x=campsis %>% mutate(DOSE=1000, TAU=24), variable="Y") %>%
  add(c(Thalf.2cpt.dist(), Thalf.2cpt.eff(), Thalf.2cpt.z())) %>%
  calculate()

table <- NCAMetricsTable() %>%
  add(nca)
table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()
```

### Example 4: Compute terminal half-live based on data

```{r, message=FALSE}
nca <- NCAMetrics(x=campsis, variable="Y") %>%
  add(c(Thalf(x=campsis %>% timerange(7*24, 10*24)))) %>%
  calculate()

table <- NCAMetricsTable() %>%
  add(nca)
table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()
```

### Example 5: Round your PK metrics

```{r, message=FALSE}
# Day 1
ncaD1 <- NCAMetrics(x=campsis %>% timerange(0, 24), variable="Y", scenario=c(day="Day 1")) %>%
  add(AUC(digits=~style_sigfig(.x, 2), name="AUC1")) %>% # At least 2 significant figures (default in gtsummary)
  add(AUC(digits=c(1,2,2), name="AUC2")) %>%             # Respectively 1/2/2 digit(s) after comma for med, p5 and p95
  add(AUC(digits=~signif(.x, 2), name="AUC3")) %>%       # 2 significant digits only
  add(AUC(digits=list(~plyr::round_any(.x, 5),
                      ~round(.x, 1) ,
                      ~style_number(.x)), name="AUC4")) %>% # 1 specific function for med, p5 and p95
  campsisnca::calculate()

# Day 7 
ncaD7 <- NCAMetrics(x=campsis %>% timerange(144, 168, rebase=TRUE), variable="Y", scenario=c(day="Day 7")) %>%
  add(AUC(name="AUC1")) %>%
  add(AUC(name="AUC2")) %>%
  add(AUC(name="AUC3")) %>%
  add(AUC(name="AUC4")) %>%
  campsisnca::calculate()

table <- NCAMetricsTable() %>%
  add(c(ncaD1, ncaD7))
  
table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()
```

### Example 6: Export custom metrics (including categorical data)

```{r, message=FALSE}
# Compute Cmax yourself using campsisnca
custom1 <- CustomMetric(fun=~Cmax() %>% iValue(.x, .y), name="Cmax custom", unit="ng/mL")

# Check if Cmax if higher than 12 ng/mL
custom2 <- CustomMetric(fun=~(Cmax() %>% iValue(.x, .y)) > 12, name="Cmax > 12", unit="%", categorical=TRUE)

# Shortcut notation is also accepted
custom3 <- CustomMetric(fun=~Cmax > 13, name="Cmax > 13", unit="%", categorical=TRUE)


# Day 1
ncaD1 <- NCAMetrics(x=campsis %>% timerange(0, 24), variable="Y", scenario=c(day="Day 1")) %>%
  add(c(Cmax(unit="ng/mL"), Tmax(unit="h"), custom1, custom2, custom3)) %>%
  campsisnca::calculate()

# Day 7 
ncaD7 <- NCAMetrics(x=campsis %>% timerange(144, 168, rebase=TRUE), variable="Y", scenario=c(day="Day 7")) %>%
  add(c(Cmax(), Tmax(), custom1, custom2, custom3)) %>%
  campsisnca::calculate()

table <- NCAMetricsTable() %>%
  add(c(ncaD1, ncaD7))

table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()

# Alternatively, all dichotomous levels can be shown as well:
table %>% export(dest="gt", subscripts=TRUE, all_dichotomous_levels=TRUE) %>% as_raw_html()
```

### Example 7: Geometric mean / Geometric CV

```{r, message=FALSE}
nca <- NCAMetrics(x=campsis, variable="Y") %>%
  add(c(AUC(unit="ng/mL*h", stat_display="{geomean} ({geocv}%)"), Cavg(unit="ng/mL", stat_display="{geomean} ({geocv}%)"))) %>%
  calculate()

table <- NCAMetricsTable() %>%
  add(nca)
  
table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()
```

### Example 8: Statistics on categorical data with more than 2 levels

```{r, message=FALSE}
  getCategory <- function(.x, .y) {
    values <- Cmax() %>% iValue(.x, .y)
    retValue <- dplyr::case_when(
      values < 10 ~ "(1) < 10 ng/mL",
      values >= 10 & values <= 15 ~ "(2) 10-15 ng/mL",
      values > 15 ~ "(3) > 15 ng/mL",
    )
    return(retValue)
  }

  # Or equivalently, the 1-line purrr-style lambda expression
  # getCategory <- ~case_when(Cmax < 10 ~ "(1) < 10 ng/mL", Cmax >= 10 & Cmax <= 15 ~ "(2) 10-15 ng/mL", Cmax > 15 ~ "(3) > 15 ng/mL")

  # Day 1
  ncaD1 <- NCAMetrics(x=campsis %>% timerange(0, 24), variable="Y", scenario=c(day="Day 1")) %>%
    add(c(Cmax(unit="ng/mL"), CustomMetric(fun=getCategory, name="Cmax categories", unit="%", categorical=TRUE))) %>%
    campsisnca::calculate()
  
  # Day 7 
  ncaD7 <- NCAMetrics(x=campsis %>% timerange(144, 168, rebase=TRUE), variable="Y", scenario=c(day="Day 7")) %>%
    add(c(Cmax(), CustomMetric(fun=getCategory, name="Cmax categories", unit="%", categorical=TRUE))) %>%
    campsisnca::calculate()
  
  table <- NCAMetricsTable()  
  table <- table %>%
    add(c(ncaD1, ncaD7))
  
table %>% export(dest="gt", subscripts=TRUE) %>% as_raw_html()
```
