---
pagetitle: "CAMPSIS NCA"
date: ""
author: ""
output: github_document
always_allow_html: true
---

# campsisnca
Analyse your simulation output using non-compartmental analysis.

## Installation
Install the latest stable release with the authentication token you have received:
  
```{r, eval=FALSE}
devtools::install_github("Calvagone/campsisnca", ref="main", auth_token="AUTH_TOKEN", force=TRUE)
```

## Basic use

```{r, results='hide', echo=F, message=F, warning=F}
library(campsis)
ds <- Dataset(50)
ds <- ds %>% add(Bolus(time=(0:6)*24, amount=1000))
ds <- ds %>% add(Observations(times=seq(0, 7*24, by=1)))
ds <- ds %>% add(Covariate("BW", UniformDistribution(50,100)))
model <- model_library$advan4_trans4
cl <- model %>% find(Equation("CL"))
model <- model %>% replace(Equation("CL", paste0(cl@rhs, "*pow(BW/70, 0.75)")))
campsis <- model %>% simulate(dataset=ds, dest="RxODE", seed=1, outvars="BW")


```

First import the `campsisnca` package:

```{r, message=FALSE}
library(campsisnca)
```

### Example 1: PK metrics at Day 1 and Day 7

Assume some results were simulated with CAMPSIS (see `campsis` dataframe) :

```{r, message=FALSE}
campsis
```

Let's calculate PK metrics at Day 1 and Day 7 as follows:

```{r, message=FALSE}
# Day 1
ncaD1 <- NCAMetrics(x=campsis %>% timerange(0, 24), variable="Y", scenario=c(day="Day 1"))
ncaD1 <- ncaD1 %>% add(c(Auc(unit="ng/mL*h"), Cmax(unit="ng/mL"), Tmax(unit="h"), Ctrough(unit="ng/mL")))
ncaD1 <- ncaD1 %>% calculate()

# Day 7 
ncaD7 <- NCAMetrics(x=campsis %>% timerange(144, 168, rebase=TRUE), variable="Y", scenario=c(day="Day 7"))
ncaD7 <- ncaD7 %>% add(c(Auc(), Cmax(), Tmax(), Ctrough()))
ncaD7 <- ncaD7 %>% calculate()
```

These 2 metrics may be imported into a metrics table object, as follows:

```{r, message=FALSE}
table <- NCAMetricsTable(unitLineBreak=TRUE)  
table <- table %>% add(c(ncaD1, ncaD7))
```

This table can be exported:

1. To a dataframe using the `export` function:

```{r, message=FALSE}
table %>% export(dest="dataframe")
```

2. To a HTML table using `kable` and format argument `html`:

```{r, message=FALSE}
table %>% export(dest="kable", format="html")
```

3. To a LaTeX table using `kable` and format argument `latex`:

```{r, eval=FALSE, message=FALSE}
table %>% export(dest="kable", format="latex")
```

### Example 2: PK metrics at Day 1 and Day 7 for different body weight ranges

```{r, message=FALSE}
library(dplyr)
campsis_bw_50_75 <- campsis %>% filter(BW > 50 & BW < 75)
campsis_bw_75_100 <- campsis %>% filter(BW >= 75 & BW < 100)

scenarioD1_a <- c(day="Day 1", bw_range="BW range: 50-75")
ncaD1_a <- NCAMetrics(x=campsis_bw_50_75 %>% timerange(0, 24), variable="Y", scenario=scenarioD1_a)
ncaD1_a <- ncaD1_a %>% add(c(Auc(unit="ng/mL*h"), Cmax(unit="ng/mL"), Tmax(unit="h"), Ctrough(unit="ng/mL")))
ncaD1_a <- ncaD1_a %>% calculate()

scenarioD7_a <- c(day="Day 7", bw_range="BW range: 50-75")
ncaD7_a <- NCAMetrics(x=campsis_bw_50_75 %>% timerange(144, 168, rebase=T), variable="Y", scenario=scenarioD7_a)
ncaD7_a <- ncaD7_a %>% add(c(Auc(), Cmax(), Tmax(), Ctrough()))
ncaD7_a <- ncaD7_a %>% calculate()

scenarioD1_b <- c(day="Day 1", bw_range="BW range: 75-100")
ncaD1_b <- NCAMetrics(x=campsis_bw_75_100 %>% timerange(0, 24), variable="Y", scenario=scenarioD1_b)
ncaD1_b <- ncaD1_b %>% add(c(Auc(), Cmax(), Tmax(), Ctrough()))
ncaD1_b <- ncaD1_b %>% calculate()

scenarioD7_b <- c(day="Day 7", bw_range="BW range: 75-100")
ncaD7_b <- NCAMetrics(x=campsis_bw_75_100 %>% timerange(144, 168, rebase=T), variable="Y", scenario=scenarioD7_b)
ncaD7_b <- ncaD7_b %>% add(c(Auc(), Cmax(), Tmax(), Ctrough()))
ncaD7_b <- ncaD7_b %>% calculate()

table <- NCAMetricsTable(unitLineBreak=TRUE)  
table <- table %>% add(c(ncaD1_a, ncaD7_a, ncaD1_b, ncaD7_b))
table %>% export(dest="kable", format="html")
```

### Example 3: Calculate 2-compartment half-life metrics

```{r, message=FALSE}
nca <- NCAMetrics(x=campsis %>% mutate(DOSE=1000, TAU=24), variable="Y", scenario=c(xx="Half-lives"))
nca <- nca %>% add(c(Thalf.2cpt.dist(), Thalf.2cpt.eff(), Thalf.2cpt.z()))
nca <- nca %>% calculate()

table <- NCAMetricsTable()  
table <- table %>% add(nca)
table %>% export(dest="kable", format="html")
```